Security of deployed Android devices

### 2014-01-13 netos2014-01-14.tex
Copy msg presentation to netos presentation to start work on it

\begin{frame}{Device Analyser collects lots of data}{}
 \begin{itemize}
  \note{}
  \item Android app installed on user devices
  \item Collects data with consent and sends it to our server
  \item Built by Daniel Wagner
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item 70 billion records, 2000 years, 16000 devices %TODO update these numbers
  \item \url{http://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=90px]{dalogo}{figures/dalogo512}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

@@

\begin{frame}{Root equivalent vulnerabilities are interesting}{}
 \begin{itemize}
  \item Root exploits break out of the sandbox.
  \note{}
  \item They allow applications to do arbitrarily bad things
  \item They are used in 37\% of malware %TODO check this figure
  \item How many devices are vulnerable to these exploits?
 \end{itemize}
\end{frame}

@@

\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.5\textwidth]{da_norm_api_small}{figures/da_norm_api}
 \pgfdeclareimage[width=0.5\textwidth]{play_norm_api_small}{figures/play_norm_api}
 \begin{center}
  \pgfuseimage{da_norm_api_small}
  \pgfuseimage{play_norm_api_small}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}

>>>>

\begin{frame}{Device Analyzer collects lots of data}{}
 \begin{itemize}
  \note{}
  \item Android app installed on user devices
  \item Collects data with consent and sends it to our server
  \item Built by Daniel Wagner
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item 70 billion records, 2000 years, 16000 devices
  \item \url{http://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=90px]{dalogo}{figures/dalogo512}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

@@

\begin{frame}{Root equivalent vulnerabilities are interesting}{}
 \begin{itemize}
  \item Root exploits break out of the sandbox.
  \note{}
  \item They allow applications to do arbitrarily bad things
  \item Malware which uses root exploits cannot be remotely removed
  \item They are used in 37\% of malware % "Dissecting Android Malware: Characterization and Evolution" at "2012 IEEE Symposium on Security and Privacy"
  \item How many devices are vulnerable to these exploits?
 \end{itemize}
\end{frame}

@@

\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.5\textwidth]{da_norm_api_small}{figures/da_norm_api}
 \pgfdeclareimage[width=0.5\textwidth]{play_norm_api_small}{figures/play_norm_api_trunc}
 \begin{center}
  \pgfuseimage{da_norm_api_small}
  \pgfuseimage{play_norm_api_small}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}
